Regular singular Volterra equations on complex domains

### 2023-08-14 reg-sing-volterra.tex
Conclude new whole kernel bound near zeta = 0
Add the conclusion and drop the old version.

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
\subsubsection{Bounds near $\zeta = 0$}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.

@@

Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$, which means that
\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
\par\color{RoyalBlue}
Condition \eqref{cond:eps-lambda} gives a bound on $\softker$, which can be made arbitrarily small by keeping $a,a'$ close enough to $\zeta=0$. Indeed, assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$

\begin{align*}
    |\softker(a,a')|&\lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}
\end{align*}

Hence, collecting these results together, we can find a constant $\sigma>\tau$ such that for $a,a'$ close enough to $\zeta=0$

\[
    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
\]
We'll use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

% \color{Tomato}

 %Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

%\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]

%Then,

%\begin{align*}
 %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
 %   &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
  %  &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
   % &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
%\end{align*}

%The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small. We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

\color{black}
\subsubsection{Bounds far from the diagonal}
Similarly, we can estimate the kernel $k$ far from $\zeta=0$. Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$

>>>>

% operator under consideration
\newcommand{\volterra}{\mathcal{V}}
\newcommand{\hardpart}{\mathcal{V}_0}
\newcommand{\softpart}{\mathcal{V}_\star}
\newcommand{\kerwhole}{k}
\newcommand{\hardker}{k_0}
\newcommand{\softker}{k_\star}
\newcommand{\solwhole}{f}
\newcommand{\solproto}{f_0}
\newcommand{\solptb}{f_\star}

@@

%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
\subsubsection{Overview}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. We'll use these bounds in Section~\ref{sec:V is a contraction}. \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else? If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
\subsubsection{Bounds near $\zeta = 0$}
When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.

@@

Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$, which means that
\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.

Putting these results together, we see that for any $\sigma > \tau$, we can ensure that
\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
by keeping $a$ and $a'$ close enough to $\zeta = 0$.
\subsubsection{Bounds far from the diagonal}
Similarly, we can estimate the kernel $k$ far from $\zeta=0$. Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$
